\vspace{-1cm}\normalsize{\textbf{Fairly Random: Impact of Winning the Toss on the Probability of Winning}}

### 2015-09-06 write_up/cricket.tex
Adding bib., url + natbib
Minor fix

\begin{comment}

@@

\begin{document}
\title{\vspace{-1.5cm}\normalsize{\textbf{Fairly Random: Impact of Winning the Toss on the Probability of Winning}}}
\author{Gaurav Sood\\\small{\href{mailto:gsood07@gmail.com}{\tt{gsood07@gmail.com}}} \and Derek Willis\\\small{\href{mailto:dwillis@gmail.com}{\tt{dwillis@gmail.com}}}}
\maketitle
\doublespacing

@@

\citep{de1998winning}, \citep{dawson2009bat}, \url{http://www.slate.com/articles/sports/sports_nut/2010/11/flipping_awesome.html}

>>>>

\usepackage{natbib}
\usepackage{url}
\begin{comment}

@@

\begin{document}
\title{\vspace{-1cm}\normalsize{\textbf{Fairly Random: Impact of Winning the Toss on the Probability of Winning}}}
\author{Gaurav Sood\\\small{\href{mailto:gsood07@gmail.com}{\tt{gsood07@gmail.com}}} \and Derek Willis\\\small{\href{mailto:dwillis@gmail.com}{\tt{dwillis@gmail.com}}}}
\maketitle
\doublespacing

@@

\citep{de1998winning}, \citep{dawson2009bat}, \citep{Weintraub2010}, \citep{Saad2015}
